
\section*{Conclusion and comparison with existing work}

CNTFET-based Triple Cascode OTAs are shown to perform better than the
conventional bulk-CMOS architecture in this work. The pure CNT-TC-OTA shows
remarkable advantages, such as a 197\% higher DC gain, a 4.61 times higher CMRR,
and figures of merit (FOM1 and FOM2) by 4.53 times and 1.21 times, respectively.
These results have been validated by HSPICE modeling, indicating that CNTFET
technology is an extremely interesting option for low-power, next-generation
smart devices, particularly when combined with adjustable design metrics.
A comprehensive overview of the performance evaluation of the this suggested
CNTFET-based TC-OTA at 32 nm technology node is provided in Table 4. This
evaluation includes a detailed comparison of designs at 45 nm that have been
previously described in existing literature. In comparison to its predecessors
in the sector, the table shows the advancements and improvements made by the
proposed CNTFET-based TC-OTA. Among the methods evaluated, the recommended
circuit's, DC gain, CMRR, slew rate and bandwidth stand out the most. Together
with the outstanding slew rate performance with low power, these characteristics
define the overall excellence of the proposed CNTFET-based TC-OTA system.

\begin{table}[H]
  \centering
  \caption{OTA performance summary and comparison with other contemporary OTAs.}
  \label{tab:ota_performance_summ}
  \renewcommand{\arraystretch}{1.3}
  \begin{adjustbox}{max width=\linewidth}
    \begin{tabularx}{\linewidth}{|>{\raggedright\arraybackslash}X|c|>{\raggedright\arraybackslash}X|>{\raggedright\arraybackslash}X|c|c|}
      \hline
      Parameters & CNTFET-OTA\cite{ref4} & CNTFET-TC-OTA\cite{ref5} & CNTFET-TC-OTA\cite{ref37} & CNT-FC-OTA \cite{ref13} & [This Work] \\ \hline
      Year & 2015 & 2015 & 2023 & 2024 & $\-$ \\ \hline
      Technology node & 45 nm & 45 nm & 45 nm & 45 nm & 32nm \\ \hline
      Supply voltage (V) & 0.9 & 0.9 & 0.9 & 0.9 & 0.9 \\ \hline
      DC gain (dB) & 40.3 & 45.33 & 48.7 & 43.50 & 75.44 \\ \hline
      Slew rate (V∕$\mu$s) & 30.4 & 20.6 & 971.1 & 1814 & 2544 \\ \hline
      Bandwidth (MHz) & 27.74 & 24.45 & 2700 & 0.19 & 3370 \\ \hline
      CMRR & 97.85 & 108 & 46.6 & 73.51 & 68.09 \\ \hline
      Average power ($\mu$W) & 82$\times$10$\-$3 & 38.35$\times$10$\-$3 & 59.85 & 7.14$\times$10$\-$9 & 38.7 \\ \hline
      Phase margin (◦) & 89.4 & 89.6 & 83 & 91 & 84.5 \\ \hline
    \end{tabularx}
  \end{adjustbox}
\end{table}

\subsection*{Conflict of Interests}

The authors declare no conflict of interest regarding the paper's publication.
